Visualization and analysis of probability distributions of large temporal data

### 2022-02-27 Rmd/05-conclusion.Rmd
Q2 Ch1 Juergen

>>>>

Another long-term goal would be to develop a comparable framework with a spatial component for analysis. Electricity data is commonly found in a spatio-temporal format with some type of area code, such as a postcode or administrative unit. Assuming that households in certain residential neighborhoods have similar energy usage patterns, future research could look into clustering and visualization methods for analyzing probability distributions of spatio-temporal data, perhaps through some variation of the glyph map.
